---
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    css: styles_flex.css
params: 
    set_title: ""
title: "`r params$set_title`"
---



```{r setup, include=FALSE}
library(flexdashboard)
library(rAmCharts)
library(antaresFlowbased)
library(manipulateWidget)
```


Errors
=====================================

```{r, echo = FALSE, eval = TRUE}
data_error <- data.table::rbindlist(lapply(1:nrow(dta), function(x){
  cbind(dta[x, list(hour, dayType)], dta[x, outFlowBased][[1]]$error)
}))

```

### Table
```{r}
data_render <- copy(data_error)
setnames(data_render, c("error1", "error2"), c("Negative error", "Positive error"))
knitr::kable(data_render)
```

### Histogram
```{r}

combineWidgets(
    plot(amHist(x = data_error$error1, main = "Negative error", export = T, xlab = "Negative error")),
    plot(amHist(x = data_error$error2, main = "Positive error", export = T, xlab = "Positive error"))
)
```


Hour 1 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 1, outFlowBased][[1]]
```

### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```

Hour 2 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 2, outFlowBased][[1]]
```

### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```

Hour 3 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 3, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```


Hour 4 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 4, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```


Hour 5 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 5, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```


Hour 6 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 6, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```


Hour 7 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 7, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```


Hour 8 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 8, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```



Hour 9 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 9, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```


Hour 10 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 10, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```


Hour 11 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 11, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```

Hour 12 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 12, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```

Hour 13 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 13, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```


Hour 14 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 14, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```



Hour 15 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 15, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```


Hour 16 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 16, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```


Hour 17 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 17, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```


Hour 18 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 18, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```

Hour 19 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 19, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```

Hour 20 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 20, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```

Hour 21 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 21, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```

Hour 22 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 22, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```

Hour 23 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 23, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```


Hour 24 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 24, outFlowBased][[1]]
```


### Negative error (belong in the historical domain but not in the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-plus")
```

### Positive error (belong in the model but not in the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-minus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = data$hour, dayType = data$dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = data$hour, dayType = data$dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = data$hour, dayType = data$dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = data$hour, dayType = data$dayType)
```


