---
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    css: styles_flex.css
params: 
    set_title: ""
title: "`r params$set_title`"
---



```{r setup, include=FALSE}
library(flexdashboard)
library(rAmCharts)
library(antaresFlowbased)
library(manipulateWidget)
```


Errors
=====================================

```{r, echo = FALSE, eval = TRUE}
data_error <- data.table::rbindlist(lapply(1:nrow(dta), function(x){
  cbind(dta[x, list(hour, dayType)], dta[x, outFlowBased][[1]]$error)
}))

```

### Table
```{r}
data_render <- copy(data_error)
setnames(data_render, c("error1", "error2"), c("Inf error", "Sup error"))
knitr::kable(data_render)
```

### Histogram
```{r}

combineWidgets(
    plot(amHist(x = data_error$error1, main = "Inf error", export = T, xlab = "Inf error")),
    plot(amHist(x = data_error$error2, main = "Sup error", export = T, xlab = "Sup error"))
)
```


Hour 1 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 1, outFlowBased][[1]]
hour <- 1
```

### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```

Hour 2 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 2, outFlowBased][[1]]
hour <- 2
```


### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```


Hour 3 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 3, outFlowBased][[1]]
hour <- 3
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```



Hour 4 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 4, outFlowBased][[1]]
hour <- 4
```


### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```



Hour 5 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 5, outFlowBased][[1]]
hour <- 5
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```


Hour 6 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 6, outFlowBased][[1]]
hour <- 6
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------


### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```


Hour 7 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 7, outFlowBased][[1]]
hour <- 7
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```



Hour 8 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 8, outFlowBased][[1]]
hour <- 8
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```


Hour 9 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 9, outFlowBased][[1]]
hour <- 9
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```


Hour 10 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 10, outFlowBased][[1]]
hour <- 10
```


### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```



Hour 11 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 11, outFlowBased][[1]]
hour <- 11
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```


Hour 12 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 12, outFlowBased][[1]]
hour <- 12
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------

### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```

Hour 13 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 13, outFlowBased][[1]]
hour <- 13
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```



Hour 14 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 14, outFlowBased][[1]]
hour <- 14
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------
### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```



Hour 15 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 15, outFlowBased][[1]]
hour <- 15
```


### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```



Hour 16 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 16, outFlowBased][[1]]
hour <- 16
```


### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------

### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```



Hour 17 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 17, outFlowBased][[1]]
hour <- 17
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------

### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```


Hour 18 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 18, outFlowBased][[1]]
hour <- 18
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```


Hour 19 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 19, outFlowBased][[1]]
hour <- 19
```


### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```


Hour 20 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 20, outFlowBased][[1]]
hour <- 20
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```

Hour 21 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 21, outFlowBased][[1]]
hour <- 21
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```

Row {data-height=650}
-----------------------------------------------------------------------

### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```


Hour 22 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 22, outFlowBased][[1]]
hour <- 22
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```


Hour 23 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 23, outFlowBased][[1]]
hour <- 23
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```



Row {data-height=650}
-----------------------------------------------------------------------

### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```


Hour 24 {data-navmenu="Hour"}
=====================================  

Row
-----------------------------------------------------------------------

```{r, echo = FALSE, eval = TRUE}
data <- dta[hour == 24, outFlowBased][[1]]
hour <- 24
```



### Inf error (points belonging to the historical domain but not to the model)

```{r}
valueBox(paste0(round(data$error$error1, 1) , "%"), icon = "ion-ios-minus")
```

### Sup error (points belonging to the model but not to the historical domain)

```{r}
valueBox(paste0(round(data$error$error2, 1) , "%"), icon = "ion-ios-plus")
```


Row {data-height=650}
-----------------------------------------------------------------------

### BE/FR
```{r}
graphFlowBased2D(data, "BE", "FR", hour = hour, dayType = dayType)
```

### DE/FR
```{r}
graphFlowBased2D(data, "DE", "FR", hour = hour, dayType = dayType)
```

Row {data-height=650}
------------------------------------------------------------------
### BE/NL {.no-padding}
```{r}
graphFlowBased2D(data, "BE", "NL", hour = hour, dayType = dayType)
```


### DE/NL
```{r}
graphFlowBased2D(data, "DE", "NL", hour = hour, dayType = dayType)
```



